A quantitative framework for investigating the reliability of network construction

### 2018-03-09 manuscript/CI_interactions.tex
old changes

    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as a network simultaneously describes species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition. To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure. While this additional information is useful (as, for example, interactions can affect changes in species abundances over time), empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts significantly with the widely recognised stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. Likewise, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. We emphasise that variability in community composition and interactions may or may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.

@@

    In this study, we formalize the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of pairwise interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength. To define the problem, we first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web. We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions [[double-check that we do this]]. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

@@

    Together, the combination of these three sources of uncertainty --interaction uncertainty, process uncertainty, and detection uncertainty-- results in a range of potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$). The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences). Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, when the interaction is feasible and would have been detected but did not occur at the local site. The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$, but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.

@@

  [[Tomas suggests removing the following because it slows down proceedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
  The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$). In this case, what can we do to pin down any of these different types of variation?

@@

   [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure. For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}. \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}). There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}. But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.

@@

  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability (Box~\ref{box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. Network data for a similar study system may, however, not be available. In that case, one might use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis sub-network). To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).

      To obtain the priors based on the Zillis sub-network, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code). Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network. After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation). For the \emph{Salix}-galler network, the prior distribution  was: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$. The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).

@@

% %DG: the following subsection could be moved to the appendix if we need to cut down
% Add to appendix.

%   \subsection*{Computing the credible interval around a probability estimate}

%       As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean. This is again straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S2}). Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases. In no case, however, does the confidence interval include 0. Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}). In other words, even with a very large data set, we will have problems in establishing that a given species pair can never interact.

%       % # R code to make the table:
%       % output=matrix(nrow=length(ns),ncol=5)
%       % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
%       % output[,1]=ns
%       % for(r in 1:nrow(output)){
%       %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
%       %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
%       %   output[r,2:3]=interval1
%       %   output[r,4:5]=interval2
%       % }

%       \begin{table}[h]
%         \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}. [Tomas notes that this is conceptually very similar to Fig.~\ref{Salix_pdfs}]}
%         \label{interval_table}
%         \begin{tabular}{l | c c | c c }
%         \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
%          & Lower bound & Upper bound \\
%         \hline
%         0   & 0.152 & 0.931 & 0.008 & 0.364 \\
%         1   & 0.110 & 0.843 & 0.007 & 0.337 \\
%         2   & 0.087 & 0.760 & 0.006 & 0.313 \\
%         5   & 0.053 & 0.573 & 0.005 & 0.258 \\
%         10  & 0.033 & 0.400 & 0.004 & 0.200 \\
%         15  & 0.023 & 0.306 & 0.003 & 0.163 \\
%         20  & 0.018 & 0.247 & 0.003 & 0.137 \\
%         25  & 0.015 & 0.208 & 0.002 & 0.119 \\
%         50  & 0.008 & 0.115 & 0.001 & 0.071 \\
%         100 & 0.004 & 0.061 & 0.001 & 0.039 \\
%         150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
%         200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
%         \hline
%         374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
%         \hline
%         \end{tabular}
%         \end{table}

@@

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}). In our dataset, the entire 95\% credible interval was (0.013, 0.049). We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed co-occurring is below 0.05. As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.

      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases. The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

@@

  \subsection*{Scaling up to network metrics}

@@

    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082$\leq$C$\leq$0.096 for the posterior webs; Fig.~\ref{posterior_webs}A). The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71 was similar to those in the posterior webs (2.53$\leq L_{\emph{Salix}} \leq$3.19; Fig~\ref{posterior_webs}C). The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67$\leq L_{galler} \leq $5.88; Fig.~\ref{posterior_webs}E). There was a more substantial difference in the nestedness of the observed and posterior webs: the observed network had NODF=0.560 while the posterior networks were more nested (1.39 $\leq NODF \leq$1.94). Even the networks sampled with a detection filter of 50\% had non-zero nestedness (Fig.~\ref{posterior_webs}G). This last result highlights the potential for the possibility for network structure to vary when considering the possibility that unobserved species pairs may interact.

%    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like ``training data"?]]
% DG: not so sure, I find it very useful because it simply illustrates the point. Nestedness will be a nice complement with lest trivial results
%%AE: If we are doing a complement here (I agree it is a bit boring) I think option c) from Alyssas mail is the most straight forward option. 
% AC: Added nestedness and replaced the Barbour data with training data from one site. Couldn't find any good published data.

    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186$\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0). When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F). Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}H); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.

@@

    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe with a total of 641 site visits. Each site visit or each unique site can be considered as a network in its own right or as an independent sample from which to build the meta-network. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
    \indent We may begin by comparing the frequency of co-occurrences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (3,986/4,992 \emph{Salix}-galler pairs and  9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B). The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites. Of those pairs that did interact, the incidence of interaction was also low (mean=12.0, variance=155 for \emph{Salix}-galler pairs; mean=4.04, variance=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}E-F).
  \caption{\emph{Salix} dataset}
  \label{box1}
\end{floatbox}

@@

  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution. In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}. Once $\alpha$ and $\beta$ are known, we can update them using our observed data. Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$. These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta. In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$). Both sets of intervals rely on prior information derived from the Zillis sub-network~\citep{Kopelke2017}.

      % % # R code to make the table:
      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
      % output=matrix(nrow=length(ns),ncol=5)
      % output[,1]=ns
      % for(r in 1:nrow(output)){
      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
      %   output[r,2:3]=interval1
      %   output[r,4:5]=interval2
      % }

        \begin{tabular}{l  c c  c c }
        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
         & Lower bound & Upper bound & Lower bound & Upper bound \\
        \hline
        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
        \hline
        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
        \hline
        \end{tabular}

@@

%DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo !

>>>>

    Representating an assemblage of species as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition. To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure. While this additional information is useful (as, for example, interactions can affect changes in species abundances over time), empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts significantly with the widely recognized stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. Likewise, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. Moreover, variability in community composition and interactions may or may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.

@@

    In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength. To define the problem, we first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web. We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions [[double-check that we do this]]. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

@@

    Together, the combination of these three sources of uncertainty --interaction uncertainty, process uncertainty, and detection uncertainty-- results in a range of potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$). The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences). Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challence since it must be decomposed into different quantities. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, when the interaction is feasible and would have been detected but did not occur at the local site. The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$, but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.

@@

  [[Tomas suggests removing the following because it slows down procedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
  The basic information that we are collecting consists of matrices of interaction partners. Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$). In this case, what can we do to pin down any of these different types of variation?

@@

   [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure. For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}. \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species. Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}). There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}. But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.

@@

  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability (Box~\ref{Box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. Network data for a similar study system may, however, not be available. In that case, one might use the first subnetwork collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single subnetwork from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis subweb). To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix SX}).

      To obtain the priors based on the Zillis subweb, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code). Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network. After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation). For the \emph{Salix}-galler network, the prior distribution  was: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$. The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis subweb were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix SX}).

@@

@@

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}). In our dataset, the entire 95\% credible interval was (0.013, 0.049). We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed cooccurring is below 0.05. To be 95\% confident that the interaction probability for these species is below 0.01 would require 139 observed co-occurrences with no interaction.

      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreasesy. The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.001 would require 15, 39, and 229 observed co-occurrances, respectively.

@@

  \subsection*{Scaling up to network metrics}
  [[Haven't added NODF or checked this yet.]]

@@

    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A). Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4$\leq L_{\emph{Salix}} \leq$29.5 and 50.6$\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%. There are two possible explanations for this discrepancy: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%. As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
%    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like ``training data"?]]
% DG: not so sure, I find it very useful because it simply illustrates the point. Nestedness will be a nice complement with lest trivial results
%%AE: If we are doing a complement here (I agree it is a bit boring) I think option c) from Alyssas mail is the most straight forward option.

    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.183$\leq$ C $\leq$ 0.196, 17.5 $\leq L_{galler} \leq$ 18.9, and 23.0 $\leq L_{natural enemy} \leq$ 24.8). When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F). The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and natural enemy species. Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network as that in~\citet{Kopelke2017} is missing many interactions. This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are likely to be masked by substantial noise resulting from sampling uncertainty.

@@

    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits. Each site visit can be considered as a network in its own right or as an independent sample from which to build the meta-network. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
    \indent We may begin by comparing the frequency of co-occurences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring and, even for species that did occur, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B). The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites. Of those pairs that did interact, the incidence of interaction was also low (mean=12.0, variance=155 for \emph{Salix}-galler pairs; mean=4.04, variance=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F).
  \caption{\emph{Salix} dataset}
  \label{box1}
\end{floatbox}

@@

  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution. In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}. Once $\alpha$ and $\beta$ are known, we can update them using our observed data. Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$. These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta. In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy paris with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$). Both sets of intervals rely on prior information from the network in~\citet{Barbour2016,Barbour2016Dryad}.

      % # R code to make the table:
      % output=matrix(nrow=length(ns),ncol=5)
      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
      % output[,1]=ns
      % for(r in 1:nrow(output)){
      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
      %   output[r,2:3]=interval1
      %   output[r,4:5]=interval2
      % }

        \begin{tabular}{l  c c  c c }
        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
         & Lower bound & Upper bound \\
        \hline
        0   & 0.152 & 0.931 & 0.008 & 0.364 \\
        1   & 0.110 & 0.843 & 0.007 & 0.337 \\
        2   & 0.087 & 0.760 & 0.006 & 0.313 \\
        5   & 0.053 & 0.573 & 0.005 & 0.258 \\
        10  & 0.033 & 0.400 & 0.004 & 0.200 \\
        15  & 0.023 & 0.306 & 0.003 & 0.163 \\
        20  & 0.018 & 0.247 & 0.003 & 0.137 \\
        25  & 0.015 & 0.208 & 0.002 & 0.119 \\
        50  & 0.008 & 0.115 & 0.001 & 0.071 \\
        100 & 0.004 & 0.061 & 0.001 & 0.039 \\
        150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
        200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
        \hline
        374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
        \hline
        \end{tabular}

@@

%DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo ! 
[[Update these two figs with Zillis data.]]
      \begin{figure}[ht]
        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases. \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component. This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
        \label{Salix_pdfs}
        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
        \end{figure}
